---
title: "FoRAGE Fitting-2"
author: "TaniaBarychka"
date: "26 February 2020"
output: html_document
---

This is to carry on fitting FoRAGE database, in particular dealing with poor fit of handling times. 


```{r echo=FALSE, warning=FALSE, message=FALSE}

library (ggplot2)
library(dplyr)          # for data manipulation
library(tidyr)          # for data shaping
library(ggpubr)
library(gridExtra)
library(car)
library(lattice)

#install.packages("devtools")
#devtools::install_github("cardiomoon/ggiraphExtra")
require(ggiraph)
require(ggiraphExtra)
#require(plyr)


#work desktop
#source("C:/Users/Tania Barychka/OneDrive/Desktop/HighstatLibV10.R")

#home desktop
source("C:/Users/Etherian/OneDrive/Desktop/HighstatLibV10.R")


#small laptop
#source("C:/Users/tatsi/OneDrive/Desktop/HighstatLibV10.R")

# Create customized color palette
library(RColorBrewer)
mycol = c(brewer.pal(name="Dark2", n = 8), brewer.pal(name="Paired", n = 6))
```



```{r echo=FALSE}
#work
#forage_db<- read.csv("C:/Users/Tania Barychka/OneDrive/Documents/Madingley Postdoc/resource_map_doi_10_5063_F17H1GTQ/data/FoRAGE_db_12_19_18_data_set.csv")

#summary(forage_db)


#home
forage_db<- read.csv("C:/Users/Etherian/OneDrive/Documents/Madingley Postdoc/resource_map_doi_10_5063_F17H1GTQ/data/FoRAGE_db_12_19_18_data_set.csv")

#laptop
#forage_db<- read.csv("C:/Users/Tania/OneDrive/Documents/Madingley Postdoc/resource_map_doi_10_5063_F17H1GTQ/data/FoRAGE_db_12_19_18_data_set.csv")

#small laptop
#forage_db<- read.csv("C:/Users/tatsi/OneDrive/Documents/Madingley Postdoc/resource_map_doi_10_5063_F17H1GTQ/data/FoRAGE_db_12_19_18_data_set.csv")

forage_db<-forage_db[-c(2084:2682),]
```

I'll begin by identifying points that appear to be outliers on the plots of log-fitted handling times vs:

- log-prey bodymass
- log-predator bodymass
- log-temperature
- residuals


Ideally, they are the same points. 

If they belong to the same group (e.g. freshwater) then I'll remove the points and re-fit to the group.

If they don't belong to the same group, I'll remove and refit.


